Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-17 doc/main_jfm.tex
touched up intro

\begin{abstract}
In this work, we study the dynamics of many-body systems immersed in a viscous fluid with a specified interparticle force. In particular, we apply a hydrophobic attraction potential (HAP) using a Janus type granular system to model lipid bilayer membranes. Coupling with an efficient integral equation method for rigid bodies in Stokes flow and an previous developed HAP solver, the deformations of a two-dimensional vesicle such as tank-treading motion and membrane ruptures can be observed under different values of the shear rate. Moreover, an efficient integral equation method is adopted for solving the screened Laplace equation and the mobility problem where it can accurately calculate hydrophobic and hydrodynamic interactions between near touched boundaries.
\end{abstract}

@@

\section{\label{intro}Introduction}
Described by de Gennes as ``another animal in soft matter physics", the Janus particle (often a spherical particle with a hydrophobic and a hydrophilic hemisphere) exhibits complex aggregate, clustering and self-assembly into meso- and macroscopic structures that are relevant to a wide range of applications in biology and bioengineering. Whether it is surface chemistry or polarity under an external field, the dynamics of Janus particles is inevitably the combination of long-range hydrodynamics interactions in the presence of short- and intermediate-range particle-particle interactions. 
Recently Fu {\it et al.} illustrated that the hydrophobic interactions between Janus particles in a viscous solvent can be used as a coarse-grained model to capture the mechanics of an elastic bilayer membrane of amphiphilic macromolecules such as lipids \cite{Fu20}. Depending on the total number of Janus particles and their geometry, in a viscous solvent, Janus particles are found to aggregate to form a micelle, a patch of bilayer membrane with open ends, and a self-enclosed bilayer membrane (a vesicle). Using a hybrid continuum model for the interactions between amphiphilic particles in a viscous solvent and formulating it in a boundary integral formulation, Fu {\it et al.} showed that the membrane granularity during fusion and fission of bilayers can be accurately captured. 
%This boundary integral formulation has inspired more recent work

In molecular dynamics (MD) simulations, the lipid bilayer membranes are often approximated by an implicit solvent coarse-grained model for lipids (as in the Martini code), where their hydrodynamic interactions are simplified by an implicit solvent. The long-range hydrodynamic interactions and the induced long-range lipid interactions can be captured by combining the Dry Martini with a lattice Boltzmann MD \cite{Brandner2019}. Brandner {\it et al.} used this methodology to simulate the hydrodynamics of a nano-sized vesicle under a shear flow, and reproduced the well-know vesicle hydrodynamics  such as tank-treading, tumbling and inter-leaflet slippage (reported from simulations of the Helfrich-type continuum model).

In this work we extend the hybrid continuum model in \cite{Fu20} for the Janus suspension to incorporate the collective hydrodynamics of a Janus suspension under various flows: a linear shear flow, an elongation flow, and a Poiseuille flow. We demonstrate that a vesicle made of Janus particles does behave like a vesicle in these flowing conditions. Furthermore we also show that the hybrid continuum model allows us to investigate the inter-leaflet slippage and rupture of a bilayer membrane due to an imposed flow.

This paper is organized as follows. In \S~\ref{sec:governing_eqs} we present the formulation for the Janus particles in a viscous fluid in the zero-Reynolds number regime. In \S~\ref{sec:IEM} we extend the hybrid continuum model for a Janus suspension to include the effects of a far-field flow via the mobility problem formulation. In \S~\ref{validation} we present validation of our model, and in \S~\ref{results} we present simulation results for a vesicle of Janus bilayer membrane under various flowing conditions. Finally we provide discussion and outlook for future directions in \S~\ref{conclusion}.~

\section{Governing  Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
We consider an $N_b$-many body collection of particles suspended in a
two-dimensional unbounded domain $\Omega$. The boundary of each particle is
denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
\cdots \cup \Gamma_{N_b}$ and $\nnu_i$ is the particle outward normal. 
Assuming the flow is Stokesian, the governing
equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eqn:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eqn:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor).
The process of finding the translational and angular velocities given a
force and torque is referred to as the mobility problem.

>>>>

\begin{abstract}
  In this work, we study the dynamics of many-body systems immersed in a
  viscous fluid with a specified interparticle force. In particular, we
  apply a hydrophobic attraction potential (HAP) using a Janus type
  granular system to model lipid bilayer membranes. Coupling with an
  efficient integral equation method for rigid bodies in Stokes flow and
  a previous developed HAP solver, the deformations of a two-dimensional
  vesicle such as tank-treading motion and membrane ruptures can be
  observed under different values of the shear rate. Moreover, an
  efficient integral equation method is adopted for solving the screened
  Laplace equation and the mobility problem where it can accurately
  calculate hydrophobic and hydrodynamic interactions between near
  touched boundaries.
\end{abstract}

@@

\section{\label{intro}Introduction}
Described by de Gennes as ``another animal in soft matter physics", the
Janus particle (often a spherical particle with a hydrophobic and a
hydrophilic hemisphere) exhibits complex aggregate, clustering, and
self-assembly into mesoscopic and macroscopic structures that are
relevant to a wide range of applications in biology and bioengineering.
Whether it is surface chemistry or polarity under an external field, the
dynamics of Janus particles is inevitably the combination of long-range
hydrodynamics interactions in the presence of short- and
intermediate-range particle-particle interactions. Recently~\cite{Fu20}
illustrated that the hydrophobic interactions between Janus particles in
a viscous solvent can be used as a coarse-grained model to capture the
mechanics of an elastic bilayer membrane of amphiphilic macromolecules
such as lipids. Depending on the total number of Janus particles and
their geometry, in a viscous solvent, Janus particles can aggregate to
form a micelle, a patch of bilayer membrane with open ends, and a
self-enclosed bilayer membrane (referred to as a Janus-vesicle). Using a
hybrid continuum model for the interactions between amphiphilic
particles in a viscous solvent and formulating it in a boundary integral
formulation,~\cite{Fu20} showed that the membrane granularity during
fusion and fission of bilayers can be accurately captured. 
%This boundary integral formulation has inspired more recent work

In molecular dynamics (MD) simulations, the lipid bilayer membranes are
often approximated by an implicit solvent coarse-grained model for
lipids (as in the Martini code), where their hydrodynamic interactions
are simplified by an implicit solvent. The long-range hydrodynamic
interactions and the induced long-range lipid interactions can be
captured by combining the Dry Martini with a lattice Boltzmann MD.
\cite{Brandner2019} used this methodology to simulate the hydrodynamics
of a nano-sized vesicle under a shear flow, and reproduced the well-know
vesicle hydrodynamics such as tank-treading, tumbling, and inter-leaflet
slippage (reported from simulations of the Helfrich-type continuum
model).

In this work we extend the hybrid continuum model in~\cite{Fu20} for the
Janus suspension to incorporate the collective hydrodynamics of a Janus
suspension under various flows: a linear shear flow, an elongation flow,
and a Poiseuille flow. We demonstrate that a vesicle made of Janus
particles does behave like a vesicle in these flowing conditions.
Furthermore we also show that the hybrid continuum model allows us to
investigate the inter-leaflet slippage and rupture of a bilayer membrane
due to an imposed flow. Finally, we compare a pair of interacting
Janus-vesicles with a continuum model of a pair of vesicles.

This paper is organized as follows. In \S~\ref{sec:governing_eqs} we
present the formulation for the Janus particles in a viscous fluid in
the zero-Reynolds number regime. In \S~\ref{sec:IEM} we extend the
hybrid continuum model for a Janus suspension to include the effects of
a far-field flow via the mobility problem formulation. In
\S~\ref{validation} we present validation of our model, and in
\S~\ref{results} we present simulation results for a single and pair of
Janus-vesicles under various flowing conditions. Finally we provide
discussion and outlook for future directions in \S~\ref{conclusion}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing  Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
We consider an $N_b$-many body collection of particles suspended in a
two-dimensional unbounded domain $\Omega$. The boundary of each particle is
denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
\cdots \cup \Gamma_{N_b}$ and $\nnu_i$ is the particle outward normal. 
Assuming the flow is Stokesian, the governing
equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eqn:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eqn:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor).
The process of finding the translational and angular velocities given a
force and torque is referred to as the mobility problem.
